### 2023-04-12 output/group_0_crimes_500m/tables/pre_treatment_covariate_tests.tex
limited analysis to pre-pandemic months

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_0_crimes_500m & 0.00 & 0.01 \\
 & pre_treatment_change_in_group_0_crimes_500m & 0.00 & 0.30 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.20 & 0.22 \\
 & job_density_2013 & 0.00 & 0.10 \\
 & med_hhinc2016 & 0.22 & 0.05 \\
 & poor_share2010 & 0.00 & 0.96 \\
 & popdensity2010 & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.47 & 0.00 \\
 & no_cause & 0.01 & 0.95 \\
 & non_payment & 0.03 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.12 & 0.00 \\
 & hasAttyP & 0.37 & 0.00 \\
 & isEntityD & 0.12 & 0.06 \\
 & isEntityP & 0.00 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Crime Incidents, 2017 & 0.00 & 0.53 \\
 & Change in Crime Incidents, 2017-2019 & 0.00 & 0.34 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.34 & 0.03 \\
 & Job density, 2013 & 0.00 & 0.29 \\
 & Median household income, 2016 & 0.06 & 0.01 \\
 & Poverty rate, 2010 & 0.00 & 0.01 \\
 & Population density, 2010 & 0.00 & 0.57 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.03 & 0.00 \\
 & Filing without cause & 0.02 & 0.16 \\
 & Filing for nonpayment & 0.00 & 0.04 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.25 & 0.00 \\
 & Plaintiff has attorney & 0.38 & 0.06 \\
 & Defendant is entity & 0.00 & 0.13 \\
 & Plaintiff is entity & 0.02 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-04-12 output/group_1_crimes_500m/tables/balance_table.tex
limited analysis to pre-pandemic months

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A}} & Total Group 1 Incidents, 2017 & 59.33 & 3.74 & 0.00 & 1.22 & 0.24 \\
 & $\Delta$ Group 1 Incidents, 2017-2019 & -14.54 & -0.44 & 0.45 & -0.35 & 0.56 \\
\cline{1-7}
\multirow[c]{3}{3cm}{\textit{Panel B}} & Job density, 2013 & 17,324.75 & 2,509.70 & 0.10 & 207.41 & 0.89 \\
 & Poverty rate, 2010 & 0.28 & -0.00 & 0.96 & 0.01 & 0.13 \\
 & Population density, 2010 & 23,285.59 & 1,452.05 & 0.00 & 479.29 & 0.27 \\
\cline{1-7}
\textit{Panel D} & Defendant is entity & 0.02 & -0.01 & 0.06 & 0.00 & 0.75 \\
\cline{1-7}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\multirow[c]{2}{.75cm}{\textit{Panel A}} & Total Group 1 Incidents, 2017 & 2.98 & 0.26 & 0.10 & 0.00 & 0.98 \\
 & $\Delta$ Group 1 Incidents, 2017-2019 & 12.72 & 0.07 & 0.92 & -0.18 & 0.79 \\
\cline{1-7}
\multirow[c]{5}{.75cm}{\textit{Panel B}} & Bachelor's degree, 2010 & 0.32 & 0.02 & 0.03 & -0.00 & 0.98 \\
 & Job density, 2013 & 17,879.13 & 2,380.87 & 0.29 & 184.04 & 0.93 \\
 & Median household income, 2016 & 47,493.96 & 3,485.70 & 0.01 & -54.60 & 0.94 \\
 & Poverty rate, 2010 & 0.28 & -0.02 & 0.01 & -0.01 & 0.22 \\
 & Population density, 2010 & 23,692.02 & 403.43 & 0.57 & -282.90 & 0.68 \\
\cline{1-7}
\bottomrule
\end{tabular}

### 2023-04-12 output/group_1_crimes_500m/tables/pre_treatment_covariate_tests.tex
limited analysis to pre-pandemic months

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_1_crimes_500m & 0.00 & 0.02 \\
 & pre_treatment_change_in_group_1_crimes_500m & 0.00 & 0.43 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
 & job_density_2013 & 0.00 & 0.10 \\
 & med_hhinc2016 & 0.00 & 0.05 \\
 & poor_share2010 & 0.00 & 0.96 \\
 & popdensity2010 & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.51 & 0.00 \\
 & no_cause & 0.02 & 0.95 \\
 & non_payment & 0.05 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.04 & 0.00 \\
 & hasAttyP & 0.52 & 0.00 \\
 & isEntityD & 0.00 & 0.06 \\
 & isEntityP & 0.34 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Group 1 Incidents, 2017 & 0.00 & 0.10 \\
 & $\Delta$ Group 1 Incidents, 2017-2019 & 0.00 & 0.92 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.00 & 0.03 \\
 & Job density, 2013 & 0.00 & 0.29 \\
 & Median household income, 2016 & 0.00 & 0.01 \\
 & Poverty rate, 2010 & 0.00 & 0.01 \\
 & Population density, 2010 & 0.01 & 0.57 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.10 & 0.00 \\
 & Filing without cause & 0.38 & 0.16 \\
 & Filing for nonpayment & 0.31 & 0.04 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.29 & 0.00 \\
 & Plaintiff has attorney & 0.33 & 0.06 \\
 & Defendant is entity & 0.52 & 0.13 \\
 & Plaintiff is entity & 0.73 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-04-12 output/group_2_crimes_500m/tables/pre_treatment_covariate_tests.tex
limited analysis to pre-pandemic months

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_2_crimes_500m & 0.00 & 0.87 \\
 & pre_treatment_change_in_group_2_crimes_500m & 0.00 & 0.67 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
 & job_density_2013 & 0.00 & 0.10 \\
 & med_hhinc2016 & 0.00 & 0.05 \\
 & poor_share2010 & 0.00 & 0.96 \\
 & popdensity2010 & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.22 & 0.00 \\
 & no_cause & 0.28 & 0.95 \\
 & non_payment & 0.09 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.84 & 0.00 \\
 & hasAttyP & 0.07 & 0.00 \\
 & isEntityD & 0.00 & 0.06 \\
 & isEntityP & 0.11 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Group 2 Incidents, 2017 & 0.00 & 0.96 \\
 & $\Delta$ Group 2 Incidents, 2017-2019 & 0.00 & 0.03 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.00 & 0.03 \\
 & Job density, 2013 & 0.00 & 0.29 \\
 & Median household income, 2016 & 0.00 & 0.01 \\
 & Poverty rate, 2010 & 0.00 & 0.01 \\
 & Population density, 2010 & 0.00 & 0.57 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.39 & 0.00 \\
 & Filing without cause & 0.70 & 0.16 \\
 & Filing for nonpayment & 0.65 & 0.04 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.86 & 0.00 \\
 & Plaintiff has attorney & 0.27 & 0.06 \\
 & Defendant is entity & 0.10 & 0.13 \\
 & Plaintiff is entity & 0.17 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-04-12 output/group_3_crimes_500m/tables/pre_treatment_covariate_tests.tex
limited analysis to pre-pandemic months

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_3_crimes_500m & 0.00 & 0.02 \\
 & pre_treatment_change_in_group_3_crimes_500m & 0.04 & 0.81 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.01 & 0.22 \\
 & job_density_2013 & 0.00 & 0.10 \\
 & med_hhinc2016 & 0.00 & 0.05 \\
 & poor_share2010 & 0.00 & 0.96 \\
 & popdensity2010 & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.75 & 0.00 \\
 & no_cause & 0.94 & 0.95 \\
 & non_payment & 0.85 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.43 & 0.00 \\
 & hasAttyP & 0.41 & 0.00 \\
 & isEntityD & 0.00 & 0.06 \\
 & isEntityP & 0.64 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Group 3 Incidents, 2017 & 0.00 & 0.16 \\
 & $\Delta$ Group 3 Incidents, 2017-2019 & 0.00 & 0.07 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.00 & 0.03 \\
 & Job density, 2013 & 0.00 & 0.29 \\
 & Median household income, 2016 & 0.00 & 0.01 \\
 & Poverty rate, 2010 & 0.00 & 0.01 \\
 & Population density, 2010 & 0.00 & 0.57 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.03 & 0.00 \\
 & Filing without cause & 0.02 & 0.16 \\
 & Filing for nonpayment & 0.00 & 0.04 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.27 & 0.00 \\
 & Plaintiff has attorney & 0.00 & 0.06 \\
 & Defendant is entity & 0.01 & 0.13 \\
 & Plaintiff is entity & 0.00 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-04-12 output/group_4_crimes_500m/tables/pre_treatment_covariate_tests.tex
limited analysis to pre-pandemic months

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_4_crimes_500m & 0.00 & 0.01 \\
 & pre_treatment_change_in_group_4_crimes_500m & 0.00 & 0.27 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
 & job_density_2013 & 0.00 & 0.10 \\
 & med_hhinc2016 & 0.00 & 0.05 \\
 & poor_share2010 & 0.00 & 0.96 \\
 & popdensity2010 & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.08 & 0.00 \\
 & no_cause & 0.00 & 0.95 \\
 & non_payment & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.26 & 0.00 \\
 & hasAttyP & 0.00 & 0.00 \\
 & isEntityD & 0.06 & 0.06 \\
 & isEntityP & 0.00 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Group 4 Incidents, 2017 & 0.00 & 0.56 \\
 & $\Delta$ Group 4 Incidents, 2017-2019 & 0.00 & 0.90 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.64 & 0.03 \\
 & Job density, 2013 & 0.00 & 0.29 \\
 & Median household income, 2016 & 0.54 & 0.01 \\
 & Poverty rate, 2010 & 0.25 & 0.01 \\
 & Population density, 2010 & 0.00 & 0.57 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.10 & 0.00 \\
 & Filing without cause & 0.28 & 0.16 \\
 & Filing for nonpayment & 0.07 & 0.04 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.31 & 0.00 \\
 & Plaintiff has attorney & 0.67 & 0.06 \\
 & Defendant is entity & 0.19 & 0.13 \\
 & Plaintiff is entity & 0.65 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-04-12 output/group_5_crimes_500m/tables/pre_treatment_covariate_tests.tex
limited analysis to pre-pandemic months

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_5_crimes_500m & 0.00 & 0.37 \\
 & pre_treatment_change_in_group_5_crimes_500m & 0.00 & 0.05 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
 & job_density_2013 & 0.00 & 0.10 \\
 & med_hhinc2016 & 0.00 & 0.05 \\
 & poor_share2010 & 0.00 & 0.96 \\
 & popdensity2010 & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.43 & 0.00 \\
 & no_cause & 0.03 & 0.95 \\
 & non_payment & 0.03 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.61 & 0.00 \\
 & hasAttyP & 0.00 & 0.00 \\
 & isEntityD & 0.00 & 0.06 \\
 & isEntityP & 0.00 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Group 5 Incidents, 2017 & 0.00 & 0.94 \\
 & $\Delta$ Group 5 Incidents, 2017-2019 & 0.00 & 0.90 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.00 & 0.03 \\
 & Job density, 2013 & 0.00 & 0.29 \\
 & Median household income, 2016 & 0.00 & 0.01 \\
 & Poverty rate, 2010 & 0.00 & 0.01 \\
 & Population density, 2010 & 0.00 & 0.57 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.98 & 0.00 \\
 & Filing without cause & 0.27 & 0.16 \\
 & Filing for nonpayment & 0.47 & 0.04 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.49 & 0.00 \\
 & Plaintiff has attorney & 0.00 & 0.06 \\
 & Defendant is entity & 0.00 & 0.13 \\
 & Plaintiff is entity & 0.00 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-04-12 output/summary_statistics/tables/summary_statistics.tex
colored map
limited analysis to pre-pandemic months

\begin{tabular}{llcccc}
\toprule
 &  & Mean & S.D. & N \\
Panel & Variable &  &  &  \\
\midrule
\multirow[c]{2}{4cm}{\textit{Panel A: Pre-treatment Outcomes}} & $\Delta$ Group 0 Incidents, 2017-2019 & -532.85 & 465.54 & 6,060 \\
 & Total Group 0 Incidents, 2017 & 4,068.25 & 2,258.29 & 6,060 \\
\cline{1-5}
\multirow[c]{5}{4cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.31 & 0.22 & 6,060 \\
 & Job density, 2013 & 14,806.08 & 40,595.37 & 6,060 \\
 & Median household income, 2016 & 47,188.87 & 24,703.65 & 6,060 \\
 & Poverty rate, 2010 & 0.28 & 0.14 & 6,060 \\
 & Population density, 2010 & 22,704.52 & 13,091.45 & 6,060 \\
\cline{1-5}
\multirow[c]{3}{4cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.17 & 0.37 & 6,060 \\
 & Filing without cause & 0.05 & 0.22 & 6,060 \\
 & Filing for nonpayment & 0.78 & 0.42 & 6,060 \\
\cline{1-5}
\multirow[c]{4}{4cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.08 & 0.27 & 6,060 \\
 & Plaintiff has attorney & 0.88 & 0.32 & 6,060 \\
 & Defendant is entity & 0.02 & 0.14 & 6,060 \\
 & Plaintiff is entity & 0.81 & 0.39 & 6,060 \\
\cline{1-5}
\multirow[c]{6}{4cm}{\textit{Panel E: Case Resolution}} & Case duration & 58.17 & 88.96 & 5,500 \\
 & Judgment by default & 0.19 & 0.39 & 6,060 \\
 & Case dismissed & 0.27 & 0.44 & 6,060 \\
 & Case heard & 0.03 & 0.17 & 6,060 \\
 & Money judgment & 1,938.57 & 5,337.87 & 6,060 \\
 & Case mediated & 0.40 & 0.49 & 6,060 \\
\cline{1-5}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llcccc}
\toprule
 &  & Mean & S.D. & N \\
Panel & Variable &  &  &  \\
\midrule
\multirow[c]{2}{4cm}{\textit{Panel A: Pre-treatment Outcomes}} & Change in Crime Incidents, 2017-2019 & -158.19 & 221.79 & 6,060 \\
 & Total Crime Incidents, 2017 & 1,179.33 & 708.44 & 6,060 \\
\cline{1-5}
\multirow[c]{5}{4cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.31 & 0.22 & 6,060 \\
 & Job density, 2013 & 14,806.08 & 40,595.37 & 6,060 \\
 & Median household income, 2016 & 47,188.87 & 24,703.65 & 6,060 \\
 & Poverty rate, 2010 & 0.28 & 0.14 & 6,060 \\
 & Population density, 2010 & 22,704.52 & 13,091.45 & 6,060 \\
\cline{1-5}
\multirow[c]{3}{4cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.17 & 0.37 & 6,060 \\
 & Filing without cause & 0.05 & 0.22 & 6,060 \\
 & Filing for nonpayment & 0.78 & 0.42 & 6,060 \\
\cline{1-5}
\multirow[c]{4}{4cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.08 & 0.27 & 6,060 \\
 & Plaintiff has attorney & 0.88 & 0.32 & 6,060 \\
 & Defendant is entity & 0.02 & 0.14 & 6,060 \\
 & Plaintiff is entity & 0.81 & 0.39 & 6,060 \\
\cline{1-5}
\multirow[c]{6}{4cm}{\textit{Panel E: Case Resolution}} & Case duration & 58.17 & 88.96 & 5,500 \\
 & Judgment by default & 0.19 & 0.39 & 6,060 \\
 & Case dismissed & 0.27 & 0.44 & 6,060 \\
 & Case heard & 0.03 & 0.17 & 6,060 \\
 & Money judgment & 1,938.57 & 5,337.87 & 6,060 \\
 & Case mediated & 0.40 & 0.49 & 6,060 \\
\cline{1-5}
\bottomrule
\end{tabular}
